\documentclass{article}
\usepackage{makeidx}
\usepackage[hidelinks]{hyperref}
\makeindex
\begin{document}
\sloppy
\title{Crossrefware documentation\thanks{This work was commissioned by
  Saint Louis University and Princeton University (Mathematics Department)}}
\author{Boris Veytsman\thanks{borisv@lk.net, boris@varphi.com}}
\maketitle
\tableofcontents

\section{Introduction}

These scripts can be used to create files for submission to Crossref,
check and add doi numbers, MathSciNet numbers and ZbMath numbers to
papers, and to convert `bbl' files to `bib' files.

Development sources and issue tracker are on github:
\url{https://github.com/borisveytsman/crossrefware}.
Releases are made on CTAN:
\url{https://ctan.org/pkg/crossrefware}
and from there included in \TeX\ Live and other distributions.

The script \path{ltx2crossrefxml} extracts information from an
\path{.rpi} files and (if it exists) \path{.bbl} files and generates an
XML file suitable for submission to crossref.org. (Crossref is the
organization that handles DOI numbers for scholarly papers.) It does not
actually do the submission, just generates the XML.

This \path{.rpi} file is written by the \path{resphilosophica} package
(\url{https://ctan.org/pkg/resphilosophica}). It can also be created by
handle.

Several scripts, \path{bibdoiadd}, \path{bibmradd} and \path{bibzbladd}
take a \path{bib} file, and add to each entry a DOI, MR or ZBL number
correspondingly, if they can find this entry in the corresponding
database.   

The \path{bbl2bib} script tries to reconstruct a \path{bib} file from the
corresponding \path{thebibliography} environment.  One can argue that
this operation is akin to reconstructing the cow from a steak.  The
way the script does it is by searching for the entry in the MR database,
and creating the corresponding Bib\TeX\ fields.

I am grateful to Josko Plazonic from Princeton Math Dept whose
(unpublished) Python script was an inspiration for this suite.

Following are manual pages for these scripts.  
